Supplement to ``Machine Learning for Mechanistic Models of Metapopulation Dynamics''

### 2023-11-17 si/si.Rnw
minor edits

<<table_params>>=
li1 <- li20(U=5,version='li20period1',for_ibpf=F)
li_par1 <- par_li(coef(li1),dir="from_li")
li3 <- li20(U=5,version='li20period3',for_ibpf=F)
li_par3 <- par_li(coef(li3),dir="from_li")

>>>>

<<table_params>>=
li1 <- li23(U=5,version='li20period1',for_ibpf=F)
li_par1 <- coef(li1)
li3 <- li23(U=5,version='li20period3',for_ibpf=F)
li_par3 <- coef(li3)
